---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BayesSPsurv

<!-- badges: start -->
[![R build status](https://github.com/Nicolas-Schmidt/spatialSPsurv/workflows/R-CMD-check/badge.svg)](https://github.com/Nicolas-Schmidt/BayesSPsurv/actions)
[![Project Status: Active – The project has reached a stable, usable
state and is being actively
developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-green.svg)](https://www.tidyverse.org/lifecycle/#stable)
`r badger::badge_devel("Nicolas-Schmidt/BayesMFSurv", "blue")`
[![License:
MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)

<!-- badges: end -->

Bayesian parametric spatial split-population survival models for clustered event processes. The models account for both structural and spatial heterogeneity among "at risk" and "immune" populations, and incorporates time-varying covariates. This package currently implements Weibull, Exponential and Log-logistic forms for the duration component, and includes functions for a series of diagnostic tests and plots to easily visualize convergence and spatial effects. The user can also create their own spatial weights matrix based on their units and adjacencies of interest, making the use of these models flexible and broadly applicable to a variety of  research areas.




Manual [__here__](https://github.com/Nicolas-Schmidt/spatialSPsurv/blob/master/man/figures/manual_BayesSPsurv.pdf).



## Installation

``` r
source("https://install-github.me/Nicolas-Schmidt/BayesSPsurv")
```



```{r, echo = FALSE, warning=FALSE, message=FALSE}
#source('data-raw/fsps.r')
library(spduration)
```


### Functions


| Function |Description |
| ----------------- | -------------------------------------------------------------- | 
|`exchangeSPsurv`|Markov Chain Monte Carlo (MCMC) to run Bayesian split population survival model with exchangeable frailties.|
|`pooledSPsurv` | Markov Chain Monte Carlo (MCMC) to run Bayesian split population survival model with no frailties|
|`spatialSPsurv`|Markov Chain Monte Carlo (MCMC) to run time-varying Bayesian split population survival model with spatial frailties.|
|`summary`|Returns a summary of exchangeSPsurv, pooledSPsurv or spatialSPsurv object via `coda::summary.mcmc`.|
|`spatial_SA`|| Generates a spatial weights matrix with units and adjacencies defined by the user. 
|`SPstats`|A function to calculate the deviance information criterion (DIC) and Log-likelihood for fitted model oupts.|




### Example


```{r, fig.width = 13, fig.height = 10, warning = FALSE}

library(BayesSPsurv)

## Data
walter <- spduration::add_duration(Walter_2015_JCR,"renewed_war", 
                                   unitID = "id", tID = "year", 
                                   freq = "year", ongoing = FALSE)
walter <- BayesSPsurv::spatial_SA(data = walter, var_ccode = "ccode", threshold = 800L)


set.seed(123456)

model <- 
    spatialSPsurv(
        duration = duration ~ fhcompor1 + lgdpl + comprehensive + victory + 
                              instabl + intensityln + ethfrac + unpko,
        immune   = cured ~ fhcompor1 + lgdpl + victory,
        Y0       = 't.0',
        LY       = 'lastyear',
        S        = 'sp_id' ,
        data     = walter[[1]],
        N        = 500,
        burn     = 10,
        thin     = 10,
        w        = c(1,1,1),
        m        = 10,
        form     = "Weibull",
        prop.var = 1e-05,
        A        = walter[[2]]
    )

print(model)

SPstats(model)

```

## Map

```{r}
spw   <- matrix(apply(model$W, 2, mean), ncol = 1, nrow = ncol(model$W))
ccode <- colnames(model$W)
ISO3  <- countrycode::countrycode(ccode,'gwn','iso3c')
spw   <- data.frame(ccode = ccode, ISO3 = ISO3, spw = spw) 
map   <- rworldmap::joinCountryData2Map(spw, joinCode = "ISO3", nameJoinColumn = "ISO3")
rworldmap::mapCountryData(map, nameColumnToPlot = 'spw')

```


```{r echo=FALSE, message=FALSE}


manual <- function(){
    old <- here::here()
    path <- here::here('man', 'figures')
    sink('noise.txt')
    devtools::build_manual(path = path)
    sink()
    setwd(path)
    invisible(file.rename(list.files(pattern="^BayesSPsurv"), 'manual_BayesSPsurv.pdf'))
    setwd(old)
    invisible(file.remove('noise.txt'))
}
manual()
```























